WASP-4 is accelerating towards the Earth

### 2020-01-16 paper/ms.tex
wrote procedure to do the M/a^2 constraints

>>>>

\subsection{Constraints on companion masses and semi-major axes}

Given a linear radial velocity trend, we can place limits on the mass
and semi-major axis of any planetary or stellar companions in the
system.
The constraints on the two parameters are degenerate: $\dot{\gamma}
\propto M_{\rm p} a^{-2}$.
Nonetheless, the additional information from the Zorro images can help
limit the available parameter space by setting an outer limit on the
semimajor axis, and a maximum brightness (and thereby mass) of any
putative companions.

The general procedure we use to derive these constraints has been developed by
\citet{wright_linear_trends_2007}, \citet{montet_trends_2014},
\citet{knutson_friends_2014}, \citet{bryan_statistics_2016,bryan_excess_2019},
and others.
For this study, we closely follow the procedure of \citet{bryan_excess_2019}.

We begin by defining a $50\times50$ grid in true planetary mass and
semimajor axis, evenly spaced from 3 to 300$\,$$M_{\rm Jup}$ and 0.5 to
500$\,$${\rm AU}$.

In each cell, we inject 500 simulated companions.

For each companion, we draw a set of orbital parameters for WASP-4b
from {\bf Table X} of \citet{bouma_wasp-4b_2019}.
Then, this orbital solution is subtracted, leaving the linear trend.

We then draw a mass and semimajor axis from log-uniform
distributions. We draw the inclination from a uniform distribution in
$\cos i$.
The eccentricity is drawn from \citet{kipping_beta_2013}'s long-period
exoplanet Beta distribution ($a=1.12$, $b=3.09$).

Given $(a_{\rm c}, M_{\rm c}, e_{\rm c}$ for each simulation companion, we then
fit for the time and argument of periastron, and velocity zero-points.

We then calculate the log-likelihood value of the best-fit solution.

We convert the resulting $50\times50\times500$ cube of log-likelihood
values to probability, and marginalize over the samples in each grid
cell to derive a probability distribution in mass and semi-major axis.

The distribution is shown in {\bf Figure~X}.
